Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2017-01-06 ms.tex
I added a plot to show the histogram of residuals.
I added a new plot for the two term posterior distribution. This time I restricted the priors so that we didn't unnecessarily fit multiple periodic solutions.

Since Equation \ref{eq:cosfit} is a poor fit to the data, as visible in Figure \ref{fig:model2Cosfit}, we also fit a two term cosine model.
In the two term model, we add a second cosine function at twice the frequency:
\begin{equation}\label{eq:cosfit2term}
F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) +  B t + C.
\end{equation}
Now there are two amplitude parameters $A_1$ and $A_2$ and two time offset parameters $t_1$ and $t_2$.
Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for this 2 term sinusoidal fit.
We assume the same priors as the 1 term sinusoidal fit with both $A_1$ and $A_2 > 0$.
The two term model appears visually to fit the data well.
The $\bar{\chi^2}$ is still 7.9, so it is not the expected 1.0.
However, the error bars are underestimated when only including photon and read noise components.
With exoplanet light curves, the standard deviation of the out-of-transit baseline flux can be used as an estimate for errors. With the brown dwarf rotation light curves, there is not flat baseline over which to measure error levels.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.7\textwidth]{corner_fit_2term.pdf}
\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit2term}.
Again, there is little correlation between the posteriors for the different parameters.
The offset parameter for second time offset $t_1$, has multiple solutions at a period of 1.95 hours.}\label{fig:post2Cosfit}
\end{centering}
\end{figure}

@@

>>>>

Since Equation \ref{eq:cosfit} is a poor fit to the data, as visible in Figure \ref{fig:model2Cosfit}, we also fit a two term cosine model.
In the two term model, we add a second cosine function at twice the frequency:
\begin{equation}\label{eq:cosfit2term}
F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) +  B t + C.
\end{equation}
Now there are two amplitude parameters $A_1$ and $A_2$ and two time offset parameters $t_1$ and $t_2$.
Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for this 2 term sinusoidal fit.
We assume the same priors as the 1 term sinusoidal fit with both $A_1$ and $A_2 > 0$.
For the time offsets, we 
The two term model appears visually to fit the data well.
The $\bar{\chi^2}$ is still 7.9, so it is not the expected 1.0.
However, the error bars are underestimated when only including photon and read noise components.
With exoplanet light curves, the standard deviation of the out-of-transit baseline flux can be used as an estimate for errors. With the brown dwarf rotation light curves, there is not flat baseline over which to measure error levels.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.7\textwidth]{corner_fit_2term.pdf}
\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit2term}.
Again, there is little correlation between the posteriors for the different parameters.}\label{fig:post2Cosfit}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{histo_resids.pdf}
\caption{Histogram of residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfit2term} from the data.}\label{fig:histoResid2Cosfit}
\end{centering}
\end{figure}
